Open-source landscape for 3D CSEM modelling

### 2020-04-09 manuscript/Manuscript.tex
Incorporate changes from Slack-chat

\tabl[btp]{codecomparison}{Caption.}{
  \centering
  \small
\begin{tabular}{lcccc}
  \toprule
  %
  Code & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
       & \href{https://empymod.github.io}{empymod.github.io}
       & \href{http://petgem.bsc.es}{petgem.bsc.es}
       & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  Installation & \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{pip}; \texttt{conda} \\
  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
  Eq. system & ? & FIT & ? & ? \\
  Comp. Dom. & frequency & frequency & frequency & frequency \& time \\
  Mesh & FE & FD & FE & FD; OcTree; CylMesh \\
  BC & ? & PEC & ? & ? \\
  Methods & ? & Diffusion & ? & ? \\
  Solver & FEniCS$^\dagger$ & \emg3d & FEniCS$^\dagger$ &
           PARDISO$^\ddagger$; SciPy \\
  %
  \bottomrule
\end{tabular}}%
%
As is visible from Table~\ref{tbl:codecomparison}, we use two finite element
codes and two finite difference codes; the finite element codes both make use
of the FEniCS solver \citep{CSE.15.Alnaes}, whereas \simpeg can use either
solvers implemented in SciPy, or the PARDISO solver \citep{FGCS.04.Schenk};
\emg3d, on the other hand, is a solver on its own.

>>>>

\tabl[btp]{codecomparison}{All codes solve Maxwell's Equations in its
  differential form (DE) and with the quasistatic approximation. We use two
  finite element codes and two finite difference codes; the finite element
  codes both make use of the FEniCS solver \citep{CSE.15.Alnaes}, whereas
  \simpeg can use either solvers implemented in SciPy or the PARDISO solver
  \citep{FGCS.04.Schenk}; \emg3d, on the other hand, is a solver on its own.}{
  \centering
  \small
\begin{tabular}{lcccc}
  \toprule
  %
  & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
       & \href{https://empymod.github.io}{empymod.github.io}
       & \href{http://petgem.bsc.es}{petgem.bsc.es}
       & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  Installation & \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{pip}; \texttt{conda} \\
  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
  Comp. Dom. & frequency & frequency & frequency & frequency \& time \\
  Method & FE & FIT & FE & FV \\
  Mesh & tetrahedral & rectilinear & tetrahedral & rectilinear; curvilinear \\
  BC & ? & PEC & ? & ? \\
  Solver & FEniCS$^\dagger$ & \emg3d & FEniCS$^\dagger$ &
           PARDISO$^\ddagger$; SciPy \\
  %
  \bottomrule
\end{tabular}}%
%
